$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-03-06 paper/e6ssm-tuning-paper.tex
rephrase comment on large mixing.

In the top panel one can see that the MSSM BM1 tuning (green curve) 
steadily climbs as the cutoff scale is increased, as one would expect
when the tuning originates from large soft masses entering from the
RGEs. The panel on the middle left confirms this, showing that the
largest tuning contributions come from $\Delta_{A_t}$ and
$\Delta_{m_{H_u}^2}$ with the former being the larger sensitivity
until $M_X\approx 10^8$ GeV at which point $\Delta_{m_{H_u}^2}$ takes
over, leading to the small kink in overall tuning which can be seen in
the green curve in the top panel. In this case we have chosen a
point with large mixing, which is known to reduce the MSSM tuning.  We
found this does not eliminate the tuning as there is still a strong
sensitivity to $A_t$, but we did find that increasing $A_t$ lead less
fine tuning overall for the points we looked at.

>>>>

In the top panel one can see that the MSSM BM1 tuning (green curve) 
steadily climbs as the cutoff scale is increased, as one would expect
when the tuning originates from large soft masses entering from the
RGEs. The panel on the middle left confirms this, showing that the
largest tuning contributions come from $\Delta_{A_t}$ and
$\Delta_{m_{H_u}^2}$ with the former being the larger sensitivity
until $M_X\approx 10^8$ GeV at which point $\Delta_{m_{H_u}^2}$ takes
over, leading to the small kink in overall tuning which can be seen in
the green curve in the top panel. In this case we have chosen a
point with large mixing, which is known to reduce the MSSM tuning.  We
found this does not eliminate the tuning as there is still a strong
sensitivity to $A_t$, but we did find that large mixing lead less
fine tuning overall for the points we examined.
